\documentclass[a4paper,11pt]{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
\usepackage[margin=1in]{geometry}%
\usepackage{enumitem}%
\usepackage{titlesec}%
\usepackage{needspace}%
\usepackage[hidelinks]{hyperref}%
\usepackage{ragged2e}%
%
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]%
\newcommand{\cvitem}[2]{\noindent\textbf{#1} \quad #2 \par}%
%
\begin{document}%
\normalsize%
\begin{center}%
{\Huge \textbf{MAACH Anass}}\\[0.3em]%
Student in Digital Information Architecture, specializing in Data/AI\\[0.3em]%
\href{mailto:anassmaachpro@gmail.com}{anassmaachpro@gmail.com}%
 \quad +212608603440 \quad %
\href{https://www.linkedin.com/in/anassmaach}{LinkedIn} \quad %
\href{https://github.com/sboof911}{GitHub}%
\end{center}%
\section*{Profile}%
Passionate about artificial intelligence, with a strong focus on reinforcement learning and automation. Proficient in Python and its data science and AI frameworks, including Pandas, PyArrow, TensorFlow, PyTorch, and Keras.  \newline Experienced with a variety of AI architectures such as LLMs, CNNs, RNNs, MLPs, and RL models.  \newline \newline Also skilled in web scraping (Requests, BeautifulSoup, Selenium), and have experience with C, C++, TypeScript, and Lua.  \newline Eager to continue growing in the AI field and contribute to innovative projects.%
\section*{Education}%
\noindent\makebox[3.5cm][l]{\textbf{2023--2025}}\begin{minipage}[t]{\dimexpr\linewidth-3.5cm\relax}Digital Information Architect in AI and Data, 1337-UM6P\end{minipage}\par%
\noindent\makebox[3.5cm][l]{\textbf{2019--2023}}\begin{minipage}[t]{\dimexpr\linewidth-3.5cm\relax}Junior Developer in Software Engineering, 1337-UM6P\end{minipage}\par%
\noindent\makebox[3.5cm][l]{\textbf{2016--2019}}\begin{minipage}[t]{\dimexpr\linewidth-3.5cm\relax}2-year University Degree in Mathematics and Computer Science, IBN ZOHR University\end{minipage}\par%
\noindent\makebox[3.5cm][l]{\textbf{2016--2016}}\begin{minipage}[t]{\dimexpr\linewidth-3.5cm\relax}Baccalaureate in Mathematical Sciences, Ibno Maja High-School\end{minipage}\par%
\section*{Professional Experience}%
\textbf{Python Developer Intern, Vanguard} \hfill May 2023 -- Oct 2023%
\begin{itemize}[leftmargin=*]%
\item Contributed to the development of Pyccel, a Python-to-C compiler.%
\item Implemented class support within the project.%
\item Participated in optimization and additional development tasks.%
\end{itemize}%
\section*{DATA SCIENCE Projects}%
\needspace{2\baselineskip}%
\noindent \textbf{Game Bot (Personal Project)}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Developed and maintained a bot that plays an online game via sockets.%
\item Currently integrating reinforcement learning for better battle performance.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{Gomoku} - \href{https://github.com/sboof911/Gomoku}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Developed a complete Gomoku game with both backend (Python) and frontend (TypeScript/React).%
\item Implemented an AI opponent using the Minimax algorithm with alpha-beta pruning and heuristics.%
\item Optimized performance by introducing memoization to avoid redundant calculations.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{Understanding Customer} - \href{https://github.com/sboof911/Understanding-customer}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Designed deep learning experiments for intent classification using RNN, LSTM, and Transformer-based models.%
\item Fine-tuned the Falconsai/intent\_classification model on custom datasets to improve accuracy.%
\item Compared preprocessing pipelines and architectures to evaluate model performance.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{MySpotify} - \href{https://github.com/sboof911/MySpotify}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Built a recommendation engine that integrates multiple strategies: baseline, content-based, and collaborative filtering.%
\item Implemented Word2Vec embeddings and MLP classifiers to model music similarity and user preferences.%
\item Developed ALS-based collaborative filtering for personalized recommendations.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{Multilayer Perceptron} - \href{https://github.com/sboof911/Multilayer-Perceptron}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Implemented a feed-forward multilayer perceptron from scratch to classify breast cancer data.%
\item Built training, evaluation, and visualization modules including accuracy and loss curves.%
\item Designed a modular prediction pipeline to validate real test cases.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{Leaffliction} - \href{https://github.com/sboof911/Leaffliction}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Developed a plant disease detection model using transfer learning with ResNet-18.%
\item Applied data augmentation (resizing, grayscale, blur) to improve model robustness.%
\item Separated training and prediction into modular scripts for easy reuse.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{Tweets} - \href{https://github.com/sboof911/tweets}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Explored NLP techniques including bag-of-words, TF-IDF, stemming, lemmatization, and stopword removal.%
\item Implemented similarity models with cosine distance and n-gram analysis.%
\item Integrated word2vec embeddings to improve semantic understanding.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{Uber} - \href{https://github.com/sboof911/Uber}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Performed time series analysis on Uber ride data to forecast demand.%
\item Implemented Triple Exponential Smoothing (TES) and ARIMA models.%
\item Engineered features such as ride counts by hour, day, and month.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{City Life} - \href{https://github.com/sboof911/City-Life}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Conducted geospatial analysis on urban mobility datasets.%
\item Applied clustering techniques to identify patterns in city ride distribution.%
\item Built interactive maps to visualize results with GeoPandas.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{Churn} - \href{https://github.com/sboof911/churn}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Implemented a fully-connected neural network to predict customer churn.%
\item Explored hidden layers, activation functions, backpropagation, and dropout.%
\item Evaluated model performance on real-world datasets.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{Fried Eggs} - \href{https://github.com/sboof911/Fried-eggs}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Introduced deep learning for computer vision tasks such as object detection and segmentation.%
\item Built pipelines for data labeling and model training.%
\item Implemented convolutional neural networks for image recognition.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{Total-perspective-vortex} - \href{https://github.com/sboof911/total-perspectivevortex}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Explored high-dimensional data processing techniques with Python.%
\item Experimented with brainwave-driven human-computer interaction.%
\item Built prototypes for interactive man-machine interfaces.%
\end{itemize}%
\section*{Software Projects}%
\needspace{2\baselineskip}%
\noindent \textbf{Minishell} - \href{https://github.com/sboof911/minishell}{Github}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Recreated a simplified Bash-like shell from scratch in C.%
\item Implemented core functionalities: built-in commands (echo, cd, pwd, export, unset, env, exit), environment variable expansion, and exit status tracking via `\$?`.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{Ft\_services} - \href{https://github.com/sboof911/ft_services}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Containerized and deployed multiple services (Nginx, MySQL, WordPress, Grafana, InfluxDB, phpMyAdmin).%
\item Used Docker Compose and Kubernetes to orchestrate a multi-service infrastructure.%
\item Automated service deployment with custom shell scripts.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{Webserv} - \href{https://github.com/sboof911/webserv}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Developed a fully functional HTTP server in C++ supporting HTTP/1.1.%
\item Handled socket programming, request parsing, and response generation.%
\item Supported CGI execution and tested compatibility with real browsers.%
\end{itemize}%
\needspace{3\baselineskip}%
\noindent \textbf{Ft\_transcendence} - \href{https://github.com/sboof911/ft_transcendence}{GitHub}%
\begin{itemize}[leftmargin=2em,label={},parsep=0pt,topsep=1em]%
\item Developed a full-stack web application with authentication, chat, and multiplayer Pong game.%
\item Backend built with NestJS and PostgreSQL, frontend with React.%
\item Integrated WebSockets for real-time interactions and containerized with Docker.%
\end{itemize}%
\section*{Skills}%
\begin{itemize}[leftmargin=*]%
\item \textbf{Programming Languages}: Python, C++, C, Lua%
\item \textbf{Frameworks}: TensorFlow, PyTorch, FastAPI%
\item \textbf{AI/ML}: CNN, LLM, RL, MLP, Agents%
\item \textbf{Tools}: Git, Docker, Linux, Kubernetes%
\end{itemize}%
\section*{Languages}%
English (Fluent)%
\newline%
%
French (Fluent)%
\newline%
%
Arabic (Native)%
\newline%
%
\section*{Hobbies}%
Making/Playing Music%
\newline%
%
Cycling%
\newline%
%
Billiards%
\newline%
%
\end{document}